\section{Fluid dynamics}
The aim of Computational fluid dynamics is to approximate numerically the physical conservation laws of newtonian physics:

\begin{itemize}

  \item conservation of mass

  \item The conservation of momentum (Newton’s second law, the rate of change of momentum equals the sum of forces acting on the fluid);

  \item The conservation of energy (first law of thermodynamics, the rate of change of energy equals the sum of rate of heat addition to and the rate of work done on the fluid).

\end{itemize}

    \subsection{Mass Conservation}

    The principle of conservation of mass is that, in a closed system, the mass remains constant. This means that fluid will move through a set region in such a way the mass is conserved. For an incompressible flow, this means that the outflows and the inflows will be equal. This can be written as
    \begin{equation} \label{eq:1}
      0 = \sum_{in} \dot{m} - \sum_{out} \dot{m}
    \end{equation} 

    Where $\dot{m}$ = mass flow rate.
    
    The mass flow rate can be written as $ \rho u A $,  for $\rho$ = density, $u$ = velocity and A is the scross sectional area of the flow. For flow in the x direction, $ A = \Delta z \Delta x $. For a two dimensional flow, $ \Delta z = 1 $, giving:

    \begin{equation} \label{eq:2}
      \dot{m}_{in} = \rho u \Delta y
    \end{equation}

    Extending this to equation \ref{eq:1}, in the x direction, for an incompressible flow we get

    \begin{equation} \label{eq:3}
      0 = \rho u_{in} \Delta y_{in} - \rho u_{out} \Delta y_{out}
    \end{equation}

    This can easily be extrapolated to three dimensions.

    In the case of the nasal cavity, this can be conceptualised in relation to the nasal cavity geometry

    \subsection{Momentum Conservation}

    Momentum conservation is based on the Newton's second law,

    \centerline{$\sum F = ma$}

    Here $m$ is the mass of the system, $a$ is its rate of acceleration, and  $\sum F$ is the sum of forces acting on the system. F can generally be divided in to body and surface forces. Rewriting the mass as the product of volume and the density, and acceleration as the first derivative of velocity:


    \begin{equation} \label{eq:4}
      \sum F_{body} + \sum F_{surface} = (\rho \Delta x \Delta y \Delta Z) \frac{DU}{Dt}
    \end{equation}

    Body forces generally include gravity, centrifugal, Coriolis and electromagnetic forces; these all act on the volume from a distance.

    Surface forces are those that act directly on the surface of a fluid element. These fluid forces include normal stress, in the x direction $\sigma_{xx}$, which is made up of pressure forces $p$ exerted on the body and normal viscous stress components $tau_{xx}$; and tangential stresses, $\tau_{xy}$ and $\tau_{xz}$.

    Summing these forces in the x direction, for a 2D fluid element we get:
    

    \begin{dmath} \label{eq:5}
      \sum F_{surface, x} = [\sigma_{xx} \Delta y \Delta z - (\frac{\delta \sigma_{xx}}{\delta x} \Delta x) \Delta y \Delta z] 
      + [(\tau_{xy} + \frac{\delta \tau_{yx}}{\delta y} \Delta y) \Delta x \Delta z - \tau_{yx} \Delta x \Delta z]  
      = - \frac{\delta \sigma_{xx}}{\delta x} \Delta x \Delta y \Delta z + \frac{\delta \tau_{yx}}{\delta y} \Delta x \Delta y \Delta z
    \end{dmath}


    Assuming that the fluid is Newtonian and isotropic, $\sigma_{xx}$ can be related to pressure $p$ and viscous stresses $\tau_{xx}$ by

    \centerline{$\sigma_{xx} = -p + \tau_{xx}$}

    For a Newtonian fluid, stress-strain relations can be described as 

    \begin{equation} \label{eq:6}
      \tau_{xx} = 2 \mu \frac{\delta u}{\delta x} \quad \tau_{yx} = \mu \frac{\delta u}{\delta y}
    \end{equation}

    Where $\mu$ is the viscocity of the fluid. Combining equations \ref{eq:4} , \ref{eq:5} and \ref{eq:6} in the x direction, and cancelling out the volume term:

    \begin{equation} \label{eq:7}
      \rho \frac{Du}{Dt} = - \frac{\delta p}{\delta x} + \mu (\frac{\delta^2 u}{\delta x^2} + \frac{\delta^2 u}{\delta y^2}) + \rho \sum F_{b}
    \end{equation}
    
    Here the acceleration term is the total derivative of u, defined as the combined local and advection inertial forces, which in two dimensions can be written as

    \begin{equation} \label{eq:8}
      \frac{Du}{Dt} = \frac{\delta u}{\delta t} + v \frac{\delta u}{\delta y} + u \frac{\delta u}{\delta x}
    \end{equation}

    combining equations \ref{eq:7} and \ref{eq:8} and dividing through by $\rho$:

    \begin{equation} \label{eq:8}
      \underbrace{\frac{\delta u}{\delta t}}_{local acceleration} + v \underbrace{\frac{\delta u}{\delta y} + u \frac{\delta u}{\delta x}}_{convection} = - \underbrace{\frac{1}{\rho} \frac{\delta p}{\delta x}}_{pressure gradient} + \underbrace{\nu (\frac{\delta^2 u}{\delta x^2} + \frac{\delta^2 u}{\delta y^2})}_{diffusion} + \underbrace{\sum F_{b}}_{body force}
    \end{equation}

    Where $\nu$ is kinematic viscocity, defined as $\frac{\mu}{\rho}$. 

    \section{Energy Conservation}

    Conservation of energy is derived from the first law of thermodynamics, that in a steady flow system the total energy of a control volume remains constant; that inflows and outflows must be equal. This can be expressed analogously to the mass conservation as 



\section{Governing Equations}

\section{Heat Transfer}
	
\section{Species Transport}
